Appendix

### 2020-04-02 manuscript/appendix.Rmd
fix cutoff eq

cowplot::plot_grid(
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tn)) + 
  geom_line(data = fit_tn_pred, aes(x = ag, y = exp(tn_pred)), 
             color = "red") +
  annotate("text", x = 24, y = 12000, label = get_formula("log(tn)", fit_tn), 
           size = 2) +
  ylab("TN (ug/L)") +
  xlab("Percent Agriculture") +
  scale_y_log10() +
  theme_cowplot(), 
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tp)) + 
    geom_line(data = fit_tp_pred, aes(x = ag, y = exp(tp_pred)), 
             color = "red") +
  annotate("text", x = 24, y = 900, label = get_formula("log(tp)", fit_tp), 
           size = 2) +
  ylab("TP (ug/L)") +
  xlab("Percent Agriculture") +
  scale_y_log10() +
  theme_cowplot()
)

>>>>

cowplot::plot_grid(
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tn)) + 
  geom_line(data = fit_tn_pred, aes(x = ag, y = exp(tn_pred)), 
             color = "red") +
  annotate("text", x = 29, y = 12000, label = get_formula("log(tn)", fit_tn), 
           size = 2) +
  ylab("TN (ug/L)") +
  xlab("Percent Agriculture") +
  scale_y_log10() +
  theme_cowplot(), 
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tp)) + 
    geom_line(data = fit_tp_pred, aes(x = ag, y = exp(tp_pred)), 
             color = "red") +
  annotate("text", x = 29, y = 900, label = get_formula("log(tp)", fit_tp), 
           size = 2) +
  ylab("TP (ug/L)") +
  xlab("Percent Agriculture") +
  scale_y_log10() +
  theme_cowplot()
)
